On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-07 AvdMomZvol_rails/Article.tex
[AMZr] A picture with cen-circ set

>>>>

\begin{figure}[h!]
\center{\includegraphics[width=0.7\linewidth]{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png}}
\parbox{0.7\linewidth}{\caption{A centered-circular PIPS of cardinality 17 and diameter 2210}
\label{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png}}
\end{figure}

On Fig.~\ref{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png} the following centered-circular PIPS is shown:
\begin{multline*}
	\sqrt{1}/1105*\{
	( 0 ; 0);
	( \pm1221025 ; 0);
	( 113953 ; 1215696);
	( -113953 ; -1215696);
	\\
	( 341887 ; 1172184);
	( -341887 ; -1172184);
	( 680225 ; 1014000);
	( -680225 ; -1014000);
	\\
	( 782977 ; -936936);
	( -782977 ; 936936);
	( 859775 ; -867000);
	( -859775 ; 867000);
	\\
	( 1073057 ; 582624);
	( -1073057 ; -582624);
	( 1198975 ; 231000);
	( -1198975 ; -231000);
\}
\end{multline*}
